\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{#1}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3}\\
\descript{#2}\hspace*{\fill}  \location{#4}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\location{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{\large{Relevant Coursework:}} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Elvis Theyo}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{elvistheyo.com}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://elvistheyo.vercel.app}
\newcommand{\yourEmail}{elvistheyo@gmail.com}
\newcommand{\yourPhone}{7629839732}
\newcommand{\githubUserName}{avocadopelvis}
\newcommand{\linkedInUserName}{elvistheyo}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \fontsize{40pt}{60pt}{\customRalewayMedium{\yourName}} \\ \vspace{1pt}
    % \customRalewayMedium
    \large\customRalewayMedium\color{headings}
    
    \faKaggle\faGithub\enspace \href{https://github.com/\githubUserName}{{\githubUserName}} $|$ 
    % \faGlobe\enspace
    % \href{\yourWebsiteLink}{\yourWebsite}  $|$ 
    \faLinkedin\enspace \href{https://www.linkedin.com/in/\linkedInUserName}{{linkedin.com/in/\linkedInUserName}} $|$
    \faEnvelope\enspace\href{mailto:\yourEmail}{{\yourEmail}}  
    % $|$  
    % \faPhone \enspace \yourPhone \enspace
    
    

\end{center}

% \hrule

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{EDUCATION}
% Put school first and degree second if your school is reputable
\educationHeading{Indian Institute of Information Technology, Gwalior}{Bachelor \& Master of Technology, Information Technology}{India}{Expected May 2024}
% Integrated B.Tech \& M.Tech, Information Technology
\vspace{5pt}

\courseWork{\\ Machine Learning \textbullet{} Natural Language Processing \textbullet{} Data Analytics \textbullet{} Data Mining \textbullet{} Database Management System  \\
Data Structures \& Algorithms \textbullet{}  Software Engineering \textbullet{} Object-Oriented Programming \textbullet{} Probability \& Statistics} 


% \sectionsep


%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------

\section{EXPERIENCE}

% \resumeHeading{Research Intern}{Siemens}{May 2023 - Aug 2023}{Remote}
% \sectionsep

\resumeHeading{Data Science Intern}{Katonic.ai}{Feb 2023 - April 2023}{Remote}
\begin{bullets}
% \item Worked on a use case for estimating delinquencies in customer invoice payments to create early warning signals.
\item Developed a predictive model for estimating customer invoice delinquencies to create early warning signals.
% providing early warning signals to mitigate financial risk \& deployed the model on the Katonic Machine Learning Operations (MLOps) platform.
\item  Performed Exploratory Data Analysis (EDA) \& utilized various boosting methods such as XGBoost, AdaBoost, etc.
\item Explored the Katonic Machine Learning Operations (MLOps) platform documentation to implement use cases.
\end{bullets}
\sectionsep

\resumeHeading{Research Intern}{Indian Institute of Technology Kharagpur}{May 2022 - July 2022}{Remote}
\begin{bullets}
\item Conducted research on the diagnosis of mental workload using electrocardiogram (ECG) signals \& Deep Learning.
\item Performed data preprocessing using pandas to convert the filtered signal data into samples of 15 seconds each.
% \item Augmented the signal data by adding noise in order to increase the size of the training dataset.
\item Implemented a Fully Connected Neural Network and a 1D Convolutional Neural Network (CNN) using PyTorch to predict the n-back task being performed by a subject \& achieved a maximum test accuracy of 75.7 \% for 1D CNN.

\end{bullets}
\sectionsep

\resumeHeading{Machine Learning Intern}{Feynn Labs}{Dec 2021 - Jan 2022}{Remote}
\begin{bullets}
\item{Developed a recommendation system to recommend books to users based on a book that they like.}
\item{Measured the relationship between two book ratings by using the {Pearson Correlation Coefficient}.}
\item{Determined the similarity between two users by implementing the k-Nearest Neighbors (kNN) Algorithm.}
\end{bullets}
% \sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{PROJECTS}

\projectHeading{Federated Learning for Medical Image Segmentation}{https://github.com/avocadopelvis/BTP}{Python, OpenCV, TensorFlow}
\location{Summer Project under: Dr. W Wilfred Godfrey}
\begin{bullets}
\item{Implemented an approach to Medical Image Segmentation using Federated Learning in order to preserve sensitive patient information, maintain data privacy and to enable collaboration between multiple research institutions.}
\item Trained various variants of the U-Net architecture on the BraTS 2020 dataset in a federated setting to determine the best model and attained comparable segmentation performance to centralized models.
\end{bullets}
\sectionsep

\projectHeading{Pandora - Therapeutic AI Assistant}{https://github.com/avocadopelvis/pandora}{Python, NLTK, TensorFlow, HTML, CSS, Flask}
% \location{Minor Project under: Dr. W Wilfred Godfrey}
\begin{bullets}
\item{Created a Deep Learning chatbot to simulate a therapist to provide emotional support to people with depression.}
\item{Utilized Natural Language Processing (NLP) techniques to perform text preprocessing on the text dataset.}
\item{Trained the text dataset on a Recurrent Neural Network (RNN) using TensorFlow \& achieved an accuracy of 91.8\%.}
% \item{Designed an interactive UI for the user to interact with the chatbot using Flask on the backend.}
\end{bullets}
\sectionsep

\projectHeading{Deep Mozart - Music Generation using Deep Learning}{https://github.com/avocadopelvis/deep-mozart}{Python, music21, TensorFlow}
\begin{bullets}
\item{Extracted notes from MIDI files containing Mozart's compositions using the music21 library and created a corpus.}
\item{Trained the corpus on Long short-term memory (LSTM) using TensorFlow \& achieved a training accuracy of 94.2\%.}
\item{Generated music from the model using a random index in the seed data as a starting point to predict the next notes.}
\end{bullets}

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------

\section{SKILLS}
\textbf{Languages: }{Python, SQL, R, LaTeX}
    \\ \vspace{2pt}
    \textbf{Tools: }{ MySQL, Linux, Git, Microsoft Excel, Google Colab, Visual Studio Code}
    \\ \vspace{2pt}
  \textbf{Libraries \& Frameworks: }{pandas, NumPy, scikit-learn, PyTorch, Keras, TensorFlow, Flask}
 \\ \vspace{2pt}
    \textbf{Machine Learning: }{Regression, Classification, Boosting, Clustering, Neural Networks (CNN, RNN, LSTM)}
    %  \\ \vspace{2pt}
    % \textbf{Deep Learning: }{Neural Network, CNN, RNN, LSTM}
\sectionsep

% A more concise alternate 
% \begin{skillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{skillList}
\end{document}